Named Entity Recognition on HTML as a web data extraction subtask

### 2018-09-18 tex/exemplo.tex
Dataset and LSTM explanation.

\title{Named Entity Recognition on HTML as an information extraction subtask}

@@

Web information extraction is the task of automatically extracting structured information
from unstructured or semi-structured web documents. The input usually consists of
web documents containing a number of predetermined entities organized in a similar 
manner and the information extraction task consists of identifying these entities
and organizing them according to a template. In this context, named entity recognition
(NER) is a subtask that aims to detect named entities in the text and classify them into 
predetermined categories such as person names, locations or organizations. Once we are able
to reliably detect the relevant entities, we may employ an information extraction 
algorithm to extract structured data. In this paper, we investigate different NER 
approaches from the perspective of web information extraction.

@@

% \begin{figure}
%   \centering
%   \includegraphics[width=0.5\textwidth]{pics/jap_osaka_lab}
%   \caption{Example of a faculty directory}
%   \label{fig:faculty_directory}
% \end{figure}
% 
% To acknowledge the complexity of this extraction task, take for example a snippet of 
% the staff page for the intelligent robotics laboratory from Osaka University shown in figure 
% \ref{fig:faculty_directory}. There is some structure to the way member profiles are arranged, 
% but the organization is rather flexible, also note that there is little text to contextualize
% each named entity.

@@

Despite being better than constructing wrappers manually, wrapper induction methods 
still suffered from a lack of expressive power and flexibility. These methods had 
trouble handling records with missing attributes or unusual structures because
patterns could only be identified if they happened at least once in the examples.

@@

In 2008, Sarawagi \cite{Sarawagi2008} produced a survey that classified wrappers in
rule-based methods, statistical methods and hybrid models, bringing together 
the fields of named entity recognition, relationship 
extraction and information extraction. The rule based methods encompass most of the 
previous models. The statistical methods convert the extraction task into a token labeling 
task, identifying the target entities through the assignment of labels as in a typical 
Named Entity Recognition task. Traditionally, Hidden Markov Models, Linear Chain Conditional 
Random Fields \cite{Lafferty2001}, and Maximum Entropy Taggers have been the usual choice 
for linear sequence tagging models.

More recently, with the advancement in Natural Language Processing and Deep Learning, 
neural models outperformed previous NER methods. Using a bidirectional Long Short-Term
Memory (LSTM) model with a Conditional Random Field (CRF) output layer, \cite{Huang2015} 
obtained 90.10 F1 score on the CoNLL 2003 corpus for named entity recognition. A similar model
by \cite{Lample2016} incorporates a Convolutional Neural Network over character embeddings
as an input to the bidirectional LSTM reaching an F-score of 90.94 at the same task. Finally, 
\cite{Ma2016} constructed word representations with the hidden layer of a bidirectional 
LSTM obtaining an F-score of 91.21. The latter two models make use of orthographic and 
morphological evidence to detect named entities, making the models less reliant on feature
engineering and surrounding words. Up to our knowledge, these models still have not been
employed at the web information extraction task.

@@

The second group is divided between domain specific methods and domain agnostic methods.
Domain specific methods are designed for extracting data about a particular 
application domain across multiple websites.
Domain specific methods integrate information about the particular application domain in the 
course of its development and thus are able to achieve superior performance in
comparison to domain agnostic methods. One example is the method of comment extraction 
from blog posts described by Kao et al. \cite{Kao2010}.

Domain agnostic methods are the most general extraction methods. They can extract
information from any application domain from multiple websites. They pose the hardest
challenge because the tool must infer data relevance without any prior training in
that particular application domain. Some examples are: ODE (\cite{Su2009}), ObjectRunner 
(\cite{Abdessalem2010}), and AMBER (\cite{Furche2012}). These approaches are more flexible but 
yield worse results than domain specific methods.

In this paper, we are exploring NLP based approaches to solve a domain specific problem.

@@

@@

A Hidden Markov tagger makes two assumptions. First, the 
probability of being in a given state depends only on a fixed number of previous states.
That is $ P(y_i|y_{i-1}x_{i-1}, y_{i-2}x_{i-2}, ..., y_1x_1) = P(y_i|y_{i-1}, y_{i-2},..., y_{i-k}) $. In fact, 
we can get much better results at the NER on HTML task by looking at trigrams
or quadrigrams instead of bigrams as in a regular Markov Model. Some 
label assignments are highly improbable, such as single token named entities separated 
by an Other label, and these kinds of patterns can be caught by a higher order Hidden
Markov Model. Second, the probability of a word depends only on its assigned label 
$ P(x_i|y_{i-1}x_{i-1}, ..., y_1x_1) = P(x_i|y_i) $. Finally, the probability 
$ P(Y|X) $ can be computed with the expression:

@@

The probabilities can be calculated via maximum likelihood estimation from the relative
frequency of labels and words in the corpus. The best sequence of labels can be computed 
with the Viterbi algorithm. However,
as we increase the order of the Markov Model ($k$ in Equation 1) this computation becomes 
exponentially more expensive. The beam-search strategy may be employed for a faster search,
but we found that for $ k \leq 3 $, the Viterbi algorithm is still viable.

@@

where $ \theta $ is the parameter vector that we are going to learn, $ f_k(y_{t-1}, y_{t}, x_t) $ 
is a feature function over the current and previous timesteps and the current word $ x_t $, and
$ Z(x) $ is a partition function that depends on the input. Linear chain conditional random fields
are more general than Hidden Markov Models because the transition from $ y_{t-1} $ to $ y_{t} $ can
depend on the current observation $ x_t $. In fact, linear chain CRFs do not assume independence 
between the input variables $ x $.

Linear Chain CRFs are a natural fit to Named Entity Recognition problems because of the
high label dependency. Therefore, sequence taggers that do not take this output dependency into
account tend to perform poorly. More recently, CRFs have been employed as the output layer
in neural models to account for the label dependency, producing significant improvement over
models that output labels independently.

@@

Ma and Hovy \cite{Ma2016} proposed adding a convolutional neural networks (CNN) layer 
on top of a bidirectional LSTM-CRF to encode character-level information in its 
character-level representation. Those character
representations are combined with word level representations and then fed to the
Bidirectional LSTM. This architecture possesses the capacity to learn morphological
token features that are extremely useful on the NER task, since similar named entities 
often present morphological similarities. This improvement obtained an F1 score of 
91.21 at the ConLL2003 dataset. In our experiments, the LSTM-CRF architecture with
CNN character representations used a one dimensional convolutional neural network with 30 
filters and a window size of three characters on top of the LSTM-CRF architecture,
the character embeddings fed to the CNN had 30 dimensions and were randomly initialized.

\cite{Lample2016} suggested using an a bidirectional LSTM to model character-level 
representations on a bidirectional LSTM-CRF. Combining both the forward and backward 
LSTM representations forming the complete character representation that is also combined 
with a word
representation as in the previous model. The forward LSTM is expected to be a better
representation of the suffix of a token, and the backward LSTM is expected to be a
better representation of the prefix of a token. This differentiates this architecture
from the CNN based approach, because CNN filters discover positional invariant
features while LSTMs can better represent suffixes and prefixes. In our experiments, 
the LSTM-CRF architecture with LSTM character embeddings used a bidirectional LSTM
with 25 hidden states, thus producing character representations with 50 dimensions.

All neural models used GloVe 100-dimensional word embeddings \cite{Pennington2014}
that were fine tuned during training. The models were trained with Stochastic Gradient 
Descent over 50 epochs using a learning rate of 0.01 and momentum 0.9.

@@

We constructed a novel dataset to evaluate the performance of multiple NER models
at the web information extraction task. The task consists of finding researcher
names in faculty directory web pages. This would be the 
first step in linking researcher profiles from university websites to their entries
in public databases such as DBLP \footnote{http://dblp.uni-trier.de/}. Unlike many
information extraction tasks, each web page in the dataset comes from a different 
university, and therefore has a different format, what makes many information
extraction systems impractical. The idea is to construct a system that is general 
enough to allow efficient name extraction from many different sources without requiring
any supervision between different websites. This task would be similar to the task of 
extracting comments from different news sources, in which we must recognize author 
names in different formattings before infering structure and extracting the structured 
tuple author, timestamp, comment, likes. Another similar example would be acquiring 
author information from different publishing platforms before extracting structured 
information in the format author, article, timestamp. Of course, similar systems
could be used to recognize different named entities in other contexts.

We collected 145 computer science faculty directory HTML pages from 42 different countries in 
multiple languages, although the English version was prefered when it was available. 
We tried to gathering web pages from each country in proportion to their number 
of universities relative to the total number of universities worldwide as in 
\footnote{https://univ.cc/world.php}. Each HTML page was preprocessed and converted to 
to the CONLL 2003 data format, that is one word per line with empty lines representing
sentence boundaries. Sentence were determined by the enclosing HTML tag, that is,
except for span, em, td, a, strong, b, font and sup, all other HTML tag closings were
considered to be sentence boundaries. This aimed to preserve the natural flow of reading
in HTML documents. 
CSS classes can be used to style those elements in very unexpected ways,
however this complexity was not encoded in the database. A proper HTML chunker poses many
challenges by itself. 
Take note that by the nature of these documents, many sentences contained
only one or two tokens.

Finally, all tokens were tagged with the IOB scheme put forward by
\cite{Ramshaw and Marcus (1995)} with a modification. O stands for Outside, 
B-PER is the beginning of a person name, I-PER inside a person name and PUNCT is any 
punctuation sign other than ".". Many name representations contain punctuation signs 
and the PUNCT label helps predicting label transitions properly, especially when using 
simpler algorithms like HMMs. A name for example never ends with a punctuation sign.
Also, 12 categorical features are present in the dataset, they are presented in table X.

Finally the dataset was divided in a training, development and test set.

Table 1 contains
a description of the data files.

@@

\begin{table}[h]
  \small
  \begin{center}
    \begin{tabular}{ |l|l| }
      \hline
      Data file & Documents & Sentences & Tokens & Names \\
      \hline
      Training    & unaccented token \\
      Training    & exact gazetteer match \\
      Training    & partial gazetteer match \\
      Development & is email \\
      Development & is number \\
      Development & is title \\
      Development & is URL \\
      Development & is capitalized \\
      Development & log name gazetteer count\\
      Development & log word gazetteer count\\
      Development & HTML tag parent + second parent \\
      Development & CSS class \\
      \hline
    \end{tabular}
  \end{center}
  \caption{Features present in the bla dataset}
  \label{tab:features}
\end{table}

@@

\subsection{Gazetteer}

\subsection{Evaluation}

Performance was measured based on the F1 score (Van Rijsbergen, 1975)
obtained in the test set. As in the ConLL dataset a named entity was
only considered correct when it was an exact match of the corresponding 
entity in the data file.

@@

@@

\end{document}

>>>>

\title{Named Entity Recognition on HTML as a web data extraction subtask}

@@

Web information extraction is the task of automatically extracting structured information
from unstructured or semi-structured web documents. The input usually consists of
web documents containing a number of predetermined entities organized in a similar 
manner and the information extraction task consists of identifying these entities
and organizing them according to a template. In this context, named entity recognition
(NER) is a subtask that aims to detect named entities in the text and classify them into 
predetermined categories such as person names, locations or organizations.

Once we are able
to reliably detect relevant entities, we may employ an information extraction 
algorithm to extract structured data. In this paper, we investigate different NER 
approaches from the perspective of web information extraction.

@@

Even if focusing on web documents, records also may
contain pure text that needs appropriate IE algorithms to extract the inherent data. Most WDE algorithms certainly can exploit the semi-structured nature of web documents, but can surely not restrict ourselves to that, because deeper processing is necessary. When looking through the algorithms and searching for the Swiss army knife, most algorithms can be ruled out for some incapability restricting the algorithms strongly. B.

@@

trouble handling records with missing attributes or unusual structures because
patterns could only be identified if they happened at least once in the examples.

@@

statistical models that tried to solve this problem.

In 2008, Sarawagi \cite{Sarawagi2008} produced a survey that classified wrappers into
rule-based methods, statistical methods and hybrid models, bringing together 
the fields of named entity recognition, relationship extraction and information extraction. 
The rule based methods encompass most of the 
previous models. The statistical methods convert the extraction task into a token labeling 
task, identifying the target entities through the assignment of labels as in a typical 
Named Entity Recognition task. Traditionally, Hidden Markov Models \cite{Leek1997, Freitag1999}, 
Linear Chain Conditional Random Fields \cite{Lafferty2001}, and Maximum Entropy Taggers 
\cite{McCallum2000} have been the usual choice for linear sequence tagging models.
More recently, with the advancement in Natural Language Processing and Deep Learning, 
neural models outperformed previous NER methods. Huang \cite{Huang2015} introduced the 
bidirectional Long Short-Term Memory (LSTM) model with a Conditional Random Field (CRF) output layer
for NER. Lample \cite{Lample2016} incorporated Convolutional Neural Network based character representations 
on top of the architecture. And Ma \cite{Ma2016} introduced
LSTM based character representations. Both obtaining improvements with systems that are less reliant
on feature engineering.

@@

The second group is divided between domain specific methods and domain agnostic methods.
Domain specific methods are designed for extracting data about a particular 
application domain across multiple websites. Domain specific methods integrate information 
about the particular application domain in the course of its development and thus are 
able to achieve superior performance in comparison to domain agnostic methods. 
Domain agnostic methods are the most general extraction methods. They can extract
information from any application domain and from multiple websites with different
templates. This problem can be decomposed into at least two subtasks: web page
segmentation, and attribute labeling. The system proposed by Zhu \cite{Zhu2005} and improved 
in \cite{Zhu2006} relies on \cite{Cai2004} to solve the web page segmentation task and 
on conditional random fields for the attribute labeling task. ObjectRunner (\cite{Abdessalem2010}) 
and AMBER (\cite{Furche2012}) rely on user provided ontologies to m

to develop entity recognizers based on 
gazetteer, knowledge bases or regular expressions.

Some systems can rely on some sort of automatic web page segmentation to
identify data blocks and then CRFs to label attributes.

Domain agnostic extraction systems may benefit the most from the recent 
advancements on NLP.

 The steps to that operate entity annotation, record 
segmentation, and data extraction
. These systems can operate with relatively noisy annotators
by

works by annotating entity instances, 
then infering templates from a sample of test pages, and extracting all instances
further improving the entity recognizers.

@@

Why are NER based approaches superior?

@@

A Hidden Markov tagger makes two assumptions. First, the 
probability of being in a given state depends only on a fixed number of previous states.
That is $ P(y_i|y_{i-1}x_{i-1}, y_{i-2}x_{i-2}, ..., y_1x_1) = P(y_i|y_{i-1}, y_{i-2},..., y_{i-k}) $. In fact, 
we can get much better results at the NER on HTML task by looking at trigrams
or quadrigrams instead of bigrams as in a regular Markov Model. Some 
label assignments are highly improbable, such as single token named entities separated 
by a common word, and these kinds of patterns can be caught by a higher order Hidden
Markov Model. Second, the probability of a word depends only on its assigned label 
$ P(x_i|y_{i-1}x_{i-1}, ..., y_1x_1) = P(x_i|y_i) $. Finally, the probability 
$ P(Y|X) $ can be computed with the expression:

@@

The probabilities can be calculated via maximum likelihood estimation from the relative
frequency of labels and words in the corpus. The best sequence of labels can be computed 
with the Viterbi algorithm. However,
as we increase the order of the Markov Model ($k$ in Equation 1) this computation becomes 
exponentially more expensive. The beam-search strategy may be employed for a faster search,
but we found that for $ k \leq 4 $, the Viterbi algorithm is still viable.

@@

where $ \theta $ is the parameter vector that we are going to learn, $ f_k(y_{t-1}, y_{t}, x_t) $ 
is a feature function over the current and previous timesteps and the current word $ x_t $, and
are more general than Hidden Markov Models because the transition from $ y_{t-1} $ to $ y_{t} $ can
depend on the current observation $ x_t $. In fact, linear chain CRFs do not assume independence 
between the input variables $ x $.

Linear Chain CRFs are a natural fit to Named Entity Recognition problems

 because of the
high label dependency. Therefore, sequence taggers that do not take this output dependency into
account tend to perform poorly. More recently, CRFs have been employed as the output layer
in neural models to account for the label dependency, producing significant improvement over
models that output labels independently.

@@

Ma and Hovy \cite{Ma2016} proposed adding a convolutional neural networks (CNN) layer 
on top of a bidirectional LSTM-CRF to encode character-level information in its 
character-level representation. Those character
representations are combined with word level representations and then fed to the
Bidirectional LSTM. This architecture possesses the capacity to learn morphological
token features that are extremely useful on the NER task, since similar named entities 
often present morphological similarities. This improvement obtained an F1 score of 
91.21 at the ConLL2003 dataset. In our experiments, the LSTM-CRF architecture with
CNN character representations used a one dimensional convolutional neural network with 30 
filters and a window size of three characters on top of the LSTM-CRF architecture,
the character embeddings fed to the CNN had 30 dimensions that were randomly initialized.

\cite{Lample2016} suggested using an a bidirectional LSTM to model character-level 
representations on a bidirectional LSTM-CRF. Combining both the forward and backward 
LSTM representations to form the character representation. This character
representation is also combined with a word representation. The forward LSTM is expected to be a better
representation of the suffix of a token, and the backward LSTM is expected to be a
better representation of the prefix of a token. This differentiates the architecture
from the CNN based approach, because CNN filters discover positional invariant
features while LSTMs can better represent suffixes and prefixes. In our experiments, 
the LSTM-CRF architecture with LSTM character embeddings was implemented with a bidirectional LSTM
with 25 hidden states, thus producing character representations with 50 dimensions.

All neural models used GloVe 100-dimensional word embeddings \cite{Pennington2014}
that were fine tuned during the training. The models were trained with Stochastic Gradient 
Descent over 50 epochs using a learning rate of 0.01 and momentum of 0.9.

@@

We constructed a novel dataset to evaluate the performance of multiple NER models
at the web information extraction task. The task consists of finding researcher
names in faculty directory web pages. This would be the 
first step in linking researcher profiles from university websites to their entries
in public databases such as DBLP \footnote{http://dblp.uni-trier.de/}. Unlike many
information extraction tasks, each web page in the dataset comes from a different 
university, and therefore has a different format, what makes many information
extraction approaches impractical. The idea is to explore systems that are general 
enough to allow efficient name extraction from many different sources without requiring
any supervision between different websites. This task would be similar to the task of 
extracting comments from different news sources, in which we must recognize author 
names in different formattings before infering structure and extracting the
tuple: author, timestamp, and comment. Another similar example would be acquiring 
author information from different publishing platforms before extracting structured 
information in the format: author, timestamp, and text. Similarly, the same systems
could be used to recognize different named entities in other contexts.

We collected 145 computer science faculty directory HTML pages from 42 different countries in 
multiple languages, although the English version was prefered when it was available. 
We tried gathering web pages from each country in proportion to their number 
of universities relative to the total number of universities worldwide as in 
\footnote{https://univ.cc/world.php}. Each HTML page was preprocessed and converted
to the CONLL 2003 data format, that is one word per line with empty lines representing
sentence boundaries. Sentences were determined by the encompassing HTML tags, that is,
except for \{ span, em, td, a, strong, b, font and sup \} tags, all other HTML closing tags were
treated as sentence boundaries. This aimed to preserve the natural flow of reading
in HTML documents. Sentences that were composed of more than 50 tokens were also chunked
according to punctuation. CSS classes can be used to style HTML elements in unexpected ways,
however this complexity was not taken into account. A proper HTML chunker poses 
many challenges by itself.

Take note that because of the type of documents present in the dataset, many sentences 
contained only one or two tokens.

Finally, all tokens were tagged using the IOB scheme put forward by
\cite{Ramshaw and Marcus (1995)} with a modification. O stands for Outside, 
B-PER is the beginning of a person name, I-PER inside a person name and PUNCT is any 
punctuation sign other than ".". Many name representations contain punctuation signs 
and the PUNCT label helps predicting label transitions properly, especially when using 
simpler algorithms like HMMs. A name for example never ends with a punctuation sign,
but it may be split by a punctuation sign.

\subsection{Data}

Finally the dataset was divided in a training, development and test set. Table 1 contains
a description of the data files.

@@

@@

Twelve categorical features were added to each token in the dataset, they are presented in table X.

\begin{table}[h]
  \small
  \begin{center}
    \begin{tabular}{ |l|l| }
      \hline
      Data file & Documents & Sentences & Tokens & Names \\
      \hline
      Training    & unaccented lowercase token \\
      Training    & exact gazetteer match \\
      Training    & partial gazetteer match \\
      Development & log name gazetteer count\\
      Development & log word gazetteer count\\
      Development & is email \\
      Development & is number \\
      Development & is honorific \\
      Development & is URL \\
      Development & is capitalized \\
      Development & HTML tag + parent \\
      Development & CSS class \\
      \hline
    \end{tabular}
  \end{center}
  \caption{Features present in the bla dataset}
  \label{tab:features}
\end{table}

The unaccented lowercase token was used as the key for the Glove-100 embedding lookup.

A gazetteer was constructed from the researcher list extracted from DBLP with 1.595.771
names. Feature 2 represents an exact match of a sequence of tokens to any of the 1.595.771 
names, and feature 3 represents a partial match. Feature 4 is the rounded logarithm of 
the frequency of a token in the gazetteer, and feature 5 is the rounded logarithm of the frequency
of a token in word corpus obtained through a random crawl in university websites.

Features 5 to 8 represent a simple regular expression match to an email, number, 
honorific or url, respectively. Feature 9 represents if a word is capitalized.

Feature 10 represents the HTML enclosing tag and its parent concatenated. Feature 11
represents all CSS classes concatenated. These features are not very useful in a general
sense, because every HTML document has a different format, so only because a named entity
occurs inside a given tag in a document we cannot say it is more likely to be so in other 
documents. However, these features can be trained with the self training strategy described
in section XXX to detect named entities in similar contexts in the same document.

@@

Performance was measured based on the F1 score (Van Rijsbergen, 1975)
obtained in the test set. A named entity was only considered correct when 
it was an exact match of the corresponding entity in the data file.

@@

\end{document}
\documentclass[sigconf]{acmart}
\settopmatter{printacmref=false} % Removes citation information below abstract
\renewcommand\footnotetextcopyrightpermission[1]{} % removes footnote with conference information in first column
\pagestyle{plain} % removes running headers
\setcopyright{none}

\usepackage{booktabs} % For formal tables
\usepackage[ruled]{algorithm2e} % For algorithms
\renewcommand{\algorithmcfname}{ALGORITHM}
\SetAlFnt{\small}
\SetAlCapFnt{\small}
\SetAlCapNameFnt{\small}
